Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-06-21 optim.tex
update the squintability measure x4

  \begin{itemize}
  \tightlist
  \item
    Use jellyfish search optimiser, or JS optimiser, not jellyfish
    optimiser (my bad for leading the way)
  \item
    ``hyper-parameter'' rather than ``hyperparameter''
  \end{itemize}
\end{itemize}

@@

Projection Pursuit (PP) is a high-dimensional data visualisation
approach that involves computing informative linear projections of data
by optimising a variety of objective functions, namely \emph{projection
pursuit index (PPI)} (\citet{hall1989polynomial},
\citet{cook1993projection}, \citet{lee2010projection},
\citet{Loperfido2018}, \citet{Loperfido2020}). Given high-dimensional
data \(X \in \mathbf{R}^{n }\times p\) and PPI \(f(\cdot)\), PP finds
the orthonormal projection matrix \(A \in \mathbf{R}^{p \times d}\) by
solving the following optimisation problem:

@@

The primary goal of this study is to investigate the performance of JSO
in the context of the PP guided tour. A series of simulation experiments
using well-recognised data sets and PPIs are conducted to yield insights
regarding the behaviour of JSO under different settings and the
sensitivity of hyper-parameter in the optimisation. Second, to observe
the performance of JSO with different types of PPI, a collection of
metrics is introduced to capture specific properties of the index
including squintability and smoothness as introduced in
\citet{laa_using_2020}. To the best of the authors' knowledge, this is
the first attempt to quantitatively measure squintability and
smoothness. Finally, the relationship between the JSO performance,
hyper-parameters tuning and various properties of PPI is analysed to
provide helpful guidance for practitioners that are using the guided
tour for high dimensional visualisation.

The rest of this paper is structured as follows.
Section~\ref{sec-background} introduces the background of the PP guided
tour and reviews existing methods in the literature.
Section~\ref{sec-theory} describes the details of JSO and introduces
metrics that measure different properties of a PPI.
Section~\ref{sec-vis} visualises the behaviour of the JSO in terms of
describes a simulation study on the performance of the JSO using
well-known data sets and index functions. Section~\ref{sec-app} displays
two sets of simulation experiments comparing the JSO with the
search-better optimiser and studies the impact of different PPI
properties on the optimisation performance. Section~\ref{sec-conclusion}
summarises the work and provides suggestions for future directions.

@@

\begin{tcolorbox}[enhanced jigsaw, bottomtitle=1mm, toprule=.15mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, toptitle=1mm, colbacktitle=quarto-callout-note-color!10!white, titlerule=0mm, rightrule=.15mm, opacityback=0, title={Algorithm: Jellyfish Optimizer Pseudo Code}, arc=.35mm, leftrule=.75mm, left=2mm, breakable, opacitybacktitle=0.6, coltitle=black, colback=white]

@@

The jellyfish hyper-parameters used are 50 jellyfishes
(\texttt{n\_jellies}) and a maximum of 50 tries (\texttt{max\_tries}).
The full data contains 50 simulations, recorded by the variable
\texttt{sim}, with different seeds (\texttt{seed}). Recorded in columns
\texttt{basis}, \texttt{index\_val}, \texttt{tries}, \texttt{loop} and
\texttt{time}, are the sampled projection basis, calculated index value,
iteration ID, jellyfish ID, and time taken to find the optimum,
respectively. The basis column records every visited basis before
comparing with the current (last) basis. If a visited basis has a
smaller index value than the current (last) one, the JS optimiser keeps
the current basis for the next iteration in the search but still records
the visited inferior basis. This data can be used to derive numerical
summaries and plots:

@@

The JS optimiser provides a new swarm-based search strategy to optimise
projection pursuit problems. Two examples are provided in this section
to demonstrate its performance. The first example compares its
performance with the search-better optimiser and explores how it behaves
with different combinations of hyper-parameters. The second example
studies the effect of optimisation properties defined in
Section~\ref{sec-theory}, along with jellyfish hyper-parameters, on the
outcome of the optimisation.

\subsection{Performance of the JS optimiser in pipe-finding
problems}\label{sec-app-1}

The performance of the JS optimiser is investigated in two folds: 1)
compare it with a commonly used optimiser: the search-better optimiser
\citep{RJ-2021-105, laa_using_2020}, and 2) examine its success rate
under different hyper-parameters (number of jellyfishes and maximum
number of tries). The projection pursuit problem used is finding the
pipe shape using the holes index, investigated by
\citet{laa_using_2020}.

@@

\caption{\label{fig-proj}Projections found by the jellyfish and search
better optimisers at each 10th quantile across 50 simulations. The
projection pursuit problem is to find the pipe shape using the holes
index in the 6, 8, 10, and 12-dimensional spaces. The JS optimiser uses
100 jellyfishes and a maximum number of tries of 100. The search better
optimiser uses a maximum of 1000 tries in each step of random sampling
step before the algorithm terminates. In the 6-D data space, the JS
optimiser always finds a clear pipe shape while the search better
optimiser also finds the pipe shape but with a wide rim. At higher data
dimensions, the JS optimiser finds a higher index value and a clearer
pipe shape across all the quantiles than the search better optimiser.}

@@

Fifty simulations are conducted with both JS and the search-better
optimiser, in four dimensions (\(d = 6, 8, 10, 12\)). The JS optimiser
uses 100 jellyfishes and 100 maximum number of tries, while the
search-better optimiser allows a maximum of 1000 samples at each
iteration before the algorithm terminates. Figure~\ref{fig-proj}
presents the final projections found by the two optimisers, broken down
by 10th quantile, faceted by the data dimension. In the 6-dimensional
data scenario, the JS optimiser consistently identifies a clear pipe
shape. The search-better optimiser also finds the pipe shape but with a
wide rim, suggesting a further polish search may be required. With
increasing dimensions, the JS optimiser may not always identify the pipe
shape due to random sampling, but it still presents a pipe shape in over
50\% of cases. When compared to the search-better optimiser, the JS
optimiser reaches higher index values and clearer pipe shapes across all
quantiles.

In the second experiment, fifty simulations are conducted at each
hyper-parameter combination to analyse its effects on the success rate
of the JS optimiser. The hyper-parameters tested include: 1) 20, 50, and
100 jellyfishes, and 2) 50 and 100 maximum number of tries. In each
simulation, the success rate is calculated as defined in
Section~\ref{sec-vis}. Figure~\ref{fig-proportion} presents the
proportion of success for each hyper-parameter combinations. As the
number of jellyfishes and maximum tries increase, the success rate also
increases. For simpler problems (6 dimensions), small parameter values
(20 jellyfishes and a maximum number of tries of 50) can already result
in high success rate, while for higher-dimensional problems (8, 10, and
12 dimensions), a combination of 100 jellyfishes and 100 maximum number
of tries is necessary for at least half of the jellyfishes to find the
optimal projection.

\subsection{Factors affecting the JS optimiser success rate:
optimisation properties and jellyfish hyper-parameters}\label{sec-app-2}

The optimisation properties, including smoothness, squintability, and
speed, offer numerical metrics to characterise the complexity of a
projection pursuit optimisation problem. This example investigates how
these metrics, along with the jellyfish search hyper-parameters (the
number of jellyfishes and the maximum number of tries), affect the
success of the JS optimiser. Simulations are conducted to obtain the
success rate across various projection pursuit problems, characterised
by shape-to-find, data dimension, and index function used, as well as
different hyper-parameter combinations. Smoothness and squintability are
calculated for each projection pursuit problem as outlined in
Section~\ref{sec-theory}. A generalised linear model is used to
construct the relationship between the success rate, jellyfish
hyper-parameters and optimisation properties.

In addition to the pipe-finding problem, a new shape, sine wave, is
investigated in 6D and 8D spaces with six indices considered:
\texttt{dcor2d\_2}, \texttt{loess2d}, \texttt{MIC}, \texttt{TIC},
\texttt{spline}, and \texttt{stringy}. Combining with two jellyfish
hyper-parameters, a total of 52 cases is produced, comprising of 24
pipe-finding cases and 28 sine-wave finding cases. For each case, the JS
optimiser is run fifty times and the success rate is calculated as in
Section~\ref{sec-app-1}.

@@

Table~\ref{tbl-mod-data} combines all the variables calculated above
(the JS optimiser success rate, jellyfish hyper-parameters, and
optimisation properties) into one table. Three preprocessing steps are
applied to the data: 1) scaling the jellyfish hyper-parameters by a
factor of 10 for interpretation, 2) creating a new binary variable
\texttt{long\_time} to indicate cases with an average run time over 30
seconds, and 3) encoding the success rate for the stringy case as 0,
since none of the 50 simulations identified the sine-wave shape. A
generalised linear model with a binomial family and a logit link
function is used to fit the data and Table~\ref{tbl-mod-output} presents
the model outputs. The model suggests that the success rate of the JS
optimiser is positively associated with the two jellyfish
hyper-parameters, as well as with smoothness and squintability. However,
being flagged with long runtime and an increase of data dimension will
reduce the success rate. The variable \texttt{squintability} and
\texttt{dimension} are significant, suggesting their importance relative
to jellyfish hyper-parameters in the optimisation success.

@@

\begin{tabular}{|>{}lll>{}r|rrr>{}r|rrrr>{}r|}
\toprule
  & shape & index & d & variance & range & smooth & nugget & $\theta_1$ & $\theta_2$ & $\theta_3$ & $\theta_4$ & squint\\
\midrule
1 & pipe & holes & 6 & 0.002 & 0.371 & 2.355 & 0.221 & 1.015 & 0.860 & 3.368 & 0.018 & 0.763\\
2 & pipe & holes & 8 & 0.000 & 0.178 & 2.189 & 0.820 & 1.014 & 0.869 & 3.264 & 0.029 & 0.740\\
3 & pipe & holes & 10 & 0.000 & 0.107 & 2.192 & 3.027 & 1.016 & 0.885 & 3.151 & 0.022 & 0.737\\
4 & pipe & holes & 12 & 0.000 & 0.148 & 2.295 & 1.581 & 1.011 & 0.878 & 3.345 & 0.004 & 0.779\\
5 & sine & MIC & 6 & 0.016 & 0.092 & 2.457 & 0.083 & 0.894 & 0.571 & 1.623 & -0.024 & 0.314\\
\addlinespace
6 & sine & MIC & 8 & 0.016 & 0.081 & 2.636 & 0.084 & 0.932 & 0.328 & 1.314 & -0.030 & 0.193\\
7 & sine & TIC & 6 & 0.124 & 0.110 & 2.444 & 0.086 & 0.951 & 0.536 & 1.719 & -0.027 & 0.330\\
8 & sine & TIC & 8 & 0.125 & 0.099 & 2.475 & 0.085 & 0.949 & 0.564 & 1.723 & -0.028 & 0.342\\
9 & sine & dcor2d & 6 & 0.034 & 0.167 & 2.663 & 0.114 & 0.954 & 1.039 & 2.742 & -0.019 & 0.737\\
10 & sine & loess2d & 6 & 0.079 & 0.336 & 1.988 & 0.309 & 1.016 & 1.039 & 2.648 & 0.080 & 0.689\\
\addlinespace
11 & sine & splines2d & 6 & 0.042 & 0.242 & 2.537 & 0.102 & 1.014 & 1.051 & 2.730 & -0.009 & 0.780\\
12 & sine & stringy & 6 & 0.000 & 0.007 & 1.536 & 38.166 & 1.045 & 0.011 & 254.734 & 0.053 & 0.739\\
\bottomrule
\end{tabular}
\endgroup{}

@@

\toprule
Index & D & Smoothness & Squintability & Num. of jellyfish & Max. Num. of tries & Prop. of success & Time\\
\midrule
MIC & 6 & 2.457 & 0.314 & 20 & 50 & 0.12 & 2.479 secs\\
MIC & 6 & 2.457 & 0.314 & 20 & 100 & 0.24 & 8.950 secs\\
MIC & 6 & 2.457 & 0.314 & 50 & 50 & 0.52 & 5.651 secs\\
MIC & 6 & 2.457 & 0.314 & 50 & 100 & 0.64 & 13.223 secs\\
MIC & 6 & 2.457 & 0.314 & 100 & 50 & 0.76 & 19.453 secs\\
\addlinespace
MIC & 8 & 2.636 & 0.193 & 20 & 50 & 0.08 & 2.566 secs\\
MIC & 8 & 2.636 & 0.193 & 20 & 100 & 0.08 & 4.960 secs\\
\bottomrule

@@

\caption{\label{tbl-mod-output}Model estimates of proportion of
jellyfish success on optimisation properties and jellyfish
hyper-parameters from the generalised linear model with a binomial
family and a logit link function. The variable smoothness,
squintability, number of jellyfish and maximum number of tries are
positively associated with the JS optimiser success rate while data
dimension and being flagged as long runtime are negatively associated
with the success rate. The variable squintability and dimension are
significant, suggesting their importance relative to jellyfish
hyper-parameters in the optimisation success.}

@@

\toprule
term & estimate & std.error & statistic & p.value\\
\midrule
Intercept & -4.523 & 5.332 & -0.848 & 0.396\\
Smoothness & 1.195 & 1.915 & 0.624 & 0.533\\
Squintability & 8.241 & 2.737 & 3.011 & 0.003\\
dimension (d) & -0.628 & 0.255 & -2.462 & 0.014\\
long time & -0.874 & 1.286 & -0.680 & 0.497\\
\addlinespace
number of jellyfish & 0.216 & 0.127 & 1.701 & 0.089\\
maximum number of tries & 0.113 & 0.150 & 0.752 & 0.452\\
\bottomrule

>>>>

  \begin{itemize}
  \tightlist
  \item
    Use jellyfish search optimiser, or JSO
  \item
    ``hyper-parameter'' rather than ``hyperparameter''
  \item
    PP index rather than PPI
  \end{itemize}
\end{itemize}

@@

Projection Pursuit (PP) is a high-dimensional data visualisation
approach that involves computing informative linear projections of data
by optimising a variety of objective functions, namely \emph{PP index}
(\citet{hall1989polynomial}, \citet{cook1993projection},
\citet{lee2010projection}, \citet{Loperfido2018},
\citet{Loperfido2020}). Given high-dimensional data
\(X \in \mathbf{R}^{n }\times p\) and the index function \(f(\cdot)\),
PP finds the orthonormal projection matrix
\(A \in \mathbf{R}^{p \times d}\) by solving the following optimisation
problem:

@@

The primary goal of this study is to investigate the performance of JSO
in the context of the Projection pursuit. A series of simulation
experiments using well-recognised data sets and PP indexes are conducted
to yield insights regarding the behaviour of JSO under different
settings and the sensitivity of hyper-parameter in the optimisation.
Second, to observe the performance of JSO with different types of PP
indexes, a collection of metrics is introduced to capture specific
properties of the index including squintability and smoothness as
introduced in \citet{laa_using_2020}. To the best of the authors'
knowledge, this is the first attempt to quantitatively measure
squintability and smoothness. Finally, the relationship between the JSO
performance, hyper-parameters tuning and various properties of PP
indexes is analysed to provide helpful guidance for practitioners that
are using the guided tour for high dimensional visualisation.

The rest of this paper is structured as follows.
Section~\ref{sec-background} introduces the background of the PP guided
tour and reviews existing methods in the literature.
Section~\ref{sec-theory} describes the details of JSO and introduces
metrics that measure different properties of PP indexes.
Section~\ref{sec-vis} visualises the behaviour of the JSO in terms of
describes a simulation study on the performance of the JSO using
well-known data sets and index functions. Section~\ref{sec-app} displays
two sets of simulation experiments comparing the JSO with the
search-better optimiser and studies the impact of different PP index
properties on the optimisation performance. Section~\ref{sec-conclusion}
summarises the work and provides suggestions for future directions.

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, coltitle=black, toptitle=1mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, left=2mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, arc=.35mm, opacityback=0, breakable, colbacktitle=quarto-callout-note-color!10!white, bottomrule=.15mm, bottomtitle=1mm, titlerule=0mm, toprule=.15mm, leftrule=.75mm, colback=white]

@@

The jellyfish hyper-parameters used are 50 jellyfishes
(\texttt{n\_jellies}) and a maximum of 50 tries (\texttt{max\_tries}).
The full data contains 50 simulations, recorded by the variable
\texttt{sim}, with different seeds (\texttt{seed}). Recorded in columns
\texttt{basis}, \texttt{index\_val}, \texttt{tries}, \texttt{loop} and
\texttt{time}, are the sampled projection basis, calculated index value,
iteration ID, jellyfish ID, and time taken to find the optimum,
respectively. The basis column records every visited basis before
comparing with the current (last) basis. If a visited basis has a
smaller index value than the current (last) one, JSO will keep the
current basis for the next iteration in the search but still records the
visited inferior basis. This data can be used to derive numerical
summaries and plots:

@@

The JSO provides a new swarm-based search strategy to optimise
projection pursuit problems. Two examples are provided in this section
to demonstrate its performance. The first example compares its
performance with the search-better optimiser and explores how it behaves
with different combinations of hyper-parameters. The second example
studies the effect of optimisation properties defined in
Section~\ref{sec-theory}, along with jellyfish hyper-parameters, on the
outcome of the optimisation.

\subsection{Performance of JSO in pipe-finding
problems}\label{sec-app-1}

The performance of JSO is investigated in two folds: 1) compare it with
a commonly used optimiser: the search-better optimiser
\citep{RJ-2021-105, laa_using_2020}, and 2) examine its success rate
under different hyper-parameters (number of jellyfishes and maximum
number of tries). The projection pursuit problem used is finding the
pipe shape using the holes index, investigated by
\citet{laa_using_2020}.

@@

\caption{\label{fig-proj}Projections found by the jellyfish and search
better optimisers at each 10th quantile across 50 simulations. The
projection pursuit problem is to find the pipe shape using the holes
index in the 6, 8, 10, and 12-dimensional spaces. The JSO uses 100
jellyfishes and a maximum number of tries of 100. The search better
optimiser uses a maximum of 1000 tries in each step of random sampling
step before the algorithm terminates. In the 6-D data space, JSO always
finds a clear pipe shape while the search better optimiser also finds
the pipe shape but with a wide rim. At higher data dimensions, JSO finds
a higher index value and a clearer pipe shape across all the quantiles
than the search better optimiser.}

@@

Fifty simulations are conducted with both JSO and the search-better , in
four dimensions (\(d = 6, 8, 10, 12\)). The JSO uses 100 jellyfishes and
100 maximum number of tries, while the search-better optimiser allows a
maximum of 1000 samples at each iteration before the algorithm
terminates. Figure~\ref{fig-proj} presents the final projections found
by the two optimisers, broken down by 10th quantile, faceted by the data
dimension. In the 6-dimensional data scenario, JSO consistently
identifies a clear pipe shape. The search-better optimiser also finds
the pipe shape but with a wide rim, suggesting a further polish search
may be required. With increasing dimensions, JSO may not always identify
the pipe shape due to random sampling, but it still presents a pipe
shape in over 50\% of cases. When compared to the search-better
optimiser, JSO reaches higher index values and clearer pipe shapes
across all quantiles.

In the second experiment, fifty simulations are conducted at each
hyper-parameter combination to analyse its effects on the success rate
of JSO . The hyper-parameters tested include: 1) 20, 50, and 100
jellyfishes, and 2) 50 and 100 maximum number of tries. In each
simulation, the success rate is calculated as defined in
Section~\ref{sec-vis}. Figure~\ref{fig-proportion} presents the
proportion of success for each hyper-parameter combinations. As the
number of jellyfishes and maximum tries increase, the success rate also
increases. For simpler problems (6 dimensions), small parameter values
(20 jellyfishes and a maximum number of tries of 50) can already result
in high success rate, while for higher-dimensional problems (8, 10, and
12 dimensions), a combination of 100 jellyfishes and 100 maximum number
of tries is necessary for at least half of the jellyfishes to find the
optimal projection.

\subsection{Factors affecting JSO success rate: optimisation properties
and jellyfish hyper-parameters}\label{sec-app-2}

The optimisation properties, including smoothness, squintability, and
speed, offer numerical metrics to characterise the complexity of a
projection pursuit optimisation problem. This example investigates how
these metrics, along with the jellyfish search hyper-parameters (the
number of jellyfishes and the maximum number of tries), affect the
success of JSO. Simulations are conducted to obtain the success rate
across various projection pursuit problems, characterised by
shape-to-find, data dimension, and index function used, as well as
different hyper-parameter combinations. Smoothness and squintability are
calculated for each projection pursuit problem as outlined in
Section~\ref{sec-theory}. A generalised linear model is used to
construct the relationship between the success rate, jellyfish
hyper-parameters and optimisation properties.

In addition to the pipe-finding problem, a new shape, sine wave, is
investigated in 6D and 8D spaces with six indices considered:
\texttt{dcor2d\_2}, \texttt{loess2d}, \texttt{MIC}, \texttt{TIC},
\texttt{spline}, and \texttt{stringy}. Combining with two jellyfish
hyper-parameters, a total of 52 cases is produced, comprising of 24
pipe-finding cases and 28 sine-wave finding cases. For each case, JSO is
run fifty times and the success rate is calculated as in
Section~\ref{sec-app-1}.

@@

Table~\ref{tbl-mod-data} combines all the variables calculated above
(the JS optimiser success rate, jellyfish hyper-parameters, and
optimisation properties) into one table. Three preprocessing steps are
applied to the data: 1) scaling the jellyfish hyper-parameters by a
factor of 10 for interpretation, 2) creating a new binary variable
\texttt{long\_time} to indicate cases with an average run time over 30
seconds, and 3) encoding the success rate for the stringy case as 0,
since none of the 50 simulations identified the sine-wave shape. A
generalised linear model with a binomial family and a logit link
function is used to fit the data and Table~\ref{tbl-mod-output} presents
the model outputs. The model suggests that the success rate of JSO is
positively associated with the two jellyfish hyper-parameters, as well
as with smoothness and squintability. However, being flagged with long
runtime and an increase of data dimension will reduce the success rate.
The variable \texttt{squintability} and \texttt{dimension} are
significant, suggesting their importance relative to jellyfish
hyper-parameters in the optimisation success.

@@

\begin{tabular}{|>{}lll>{}r|rrr>{}r|rrrr>{}r|}
\toprule
  & shape & index & d & variance & range & smooth & nugget & $\theta_1$ & $\theta_2$ & $\theta_3$ & $\theta_4$ & squint\\
\midrule
1 & pipe & holes & 6 & 0.002 & 0.371 & 2.355 & 0.221 & 1.015 & 0.860 & 3.368 & 0.018 & 3.053\\
2 & pipe & holes & 8 & 0.000 & 0.178 & 2.189 & 0.820 & 1.014 & 0.869 & 3.264 & 0.029 & 2.960\\
3 & pipe & holes & 10 & 0.000 & 0.107 & 2.192 & 3.027 & 1.016 & 0.885 & 3.151 & 0.022 & 2.948\\
4 & pipe & holes & 12 & 0.000 & 0.148 & 2.295 & 1.581 & 1.011 & 0.878 & 3.345 & 0.004 & 3.117\\
5 & sine & MIC & 6 & 0.016 & 0.092 & 2.457 & 0.083 & 0.894 & 0.571 & 1.623 & -0.024 & 1.257\\
\addlinespace
6 & sine & MIC & 8 & 0.016 & 0.081 & 2.636 & 0.084 & 0.932 & 0.328 & 1.314 & -0.030 & 0.772\\
7 & sine & TIC & 6 & 0.124 & 0.110 & 2.444 & 0.086 & 0.951 & 0.536 & 1.719 & -0.027 & 1.322\\
8 & sine & TIC & 8 & 0.125 & 0.099 & 2.475 & 0.085 & 0.949 & 0.564 & 1.723 & -0.028 & 1.369\\
9 & sine & dcor2d & 6 & 0.034 & 0.167 & 2.663 & 0.114 & 0.954 & 1.039 & 2.742 & -0.019 & 2.947\\
10 & sine & loess2d & 6 & 0.079 & 0.336 & 1.988 & 0.309 & 1.016 & 1.039 & 2.648 & 0.080 & 2.756\\
\addlinespace
11 & sine & splines2d & 6 & 0.042 & 0.242 & 2.537 & 0.102 & 1.014 & 1.051 & 2.730 & -0.009 & 3.118\\
12 & sine & stringy & 6 & 0.000 & 0.007 & 1.536 & 38.166 & 1.045 & 0.011 & 254.734 & 0.053 & 2.957\\
\bottomrule
\end{tabular}
\endgroup{}

@@

\toprule
Index & D & Smoothness & Squintability & Num. of jellyfish & Max. Num. of tries & Prop. of success & Time\\
\midrule
MIC & 6 & 2.457 & 1.257 & 20 & 50 & 0.12 & 2.479 secs\\
MIC & 6 & 2.457 & 1.257 & 20 & 100 & 0.24 & 8.950 secs\\
MIC & 6 & 2.457 & 1.257 & 50 & 50 & 0.52 & 5.651 secs\\
MIC & 6 & 2.457 & 1.257 & 50 & 100 & 0.64 & 13.223 secs\\
MIC & 6 & 2.457 & 1.257 & 100 & 50 & 0.76 & 19.453 secs\\
\addlinespace
MIC & 8 & 2.636 & 0.772 & 20 & 50 & 0.08 & 2.566 secs\\
MIC & 8 & 2.636 & 0.772 & 20 & 100 & 0.08 & 4.960 secs\\
\bottomrule

@@

\caption{\label{tbl-mod-output}Model estimates of proportion of
jellyfish success on optimisation properties and jellyfish
hyper-parameters from the generalised linear model with a binomial
family and a logit link function. The variable smoothness,
squintability, number of jellyfish and maximum number of tries are
positively associated with JSO success rate while data dimension and
being flagged as long runtime are negatively associated with the success
rate. The variable squintability and dimension are significant,
suggesting their importance relative to jellyfish hyper-parameters in
the optimisation success.}

@@

\toprule
term & estimate & std.error & statistic & p.value\\
\midrule
Intercept & -4.523 & 5.332 & -0.848 & 0.396\\
Smoothness & 1.195 & 1.915 & 0.624 & 0.533\\
Squintability & 2.060 & 0.684 & 3.011 & 0.003\\
dimension (d) & -0.628 & 0.255 & -2.462 & 0.014\\
long time & -0.874 & 1.286 & -0.680 & 0.497\\
\addlinespace
number of jellyfish & 0.216 & 0.127 & 1.701 & 0.089\\
maximum number of tries & 0.113 & 0.150 & 0.752 & 0.452\\
\bottomrule
